Testing and Isolation Efficacy:\\Insights from a Simple Epidemic Model

### 2021-07-14 cover.tex
cover let

%% data macros
\input{data_macros.tex}

@@

Age is the most salient clinical indicator of risk from COVID-19 for
most patients. While age-specific distributions of known SARS-CoV-2
infections and COVID-19-related deaths have been widely reported,
relatively few sources present age distributions of hospitalizations
and serious healthcare interventions administered to COVID-19
patients. In our study, we analysed \nccmpresolved{} known SARS-CoV-2 infection
records for the province of Ontario, and quantified the age-intervention associations
for hospitalization, ICU admission, intubations, and ventilations. We
quantified existing age-related impacts of COVID-19 and identified
potential future risks should the healthcare system become overwhelmed
with COVID-19 patients.

>>>>

%% data macros
% \input{data_macros.tex}

@@

Age is the most salient clinical indicator of risk from COVID-19 for
most patients. While age-specific distributions of known SARS-CoV-2
infections and COVID-19-related deaths have been widely reported,
relatively few sources present age distributions of hospitalizations
and serious healthcare interventions administered to COVID-19
patients. In our study, we analysed known SARS-CoV-2 infection
records for the province of Ontario, and quantified the age-intervention associations
for hospitalization, ICU admission, intubations, and ventilations. We
quantified existing age-related impacts of COVID-19 and identified
potential future risks should the healthcare system become overwhelmed
with COVID-19 patients.
